\documentclass{article}
\usepackage[british]{babel}
\usepackage{geometry,amsmath,hyperref}
\geometry{left=3.17cm, bottom=2.54cm, left=3.17cm, right=3.17cm, top=2.54cm}

%%%%%%%%%% Start TeXmacs macros
\newcommand{\tmtextbf}[1]{\text{{\bfseries{#1}}}}
\newenvironment{itemizedot}{\begin{itemize} \renewcommand{\labelitemi}{$\bullet$}\renewcommand{\labelitemii}{$\bullet$}\renewcommand{\labelitemiii}{$\bullet$}\renewcommand{\labelitemiv}{$\bullet$}}{\end{itemize}}
%%%%%%%%%% End TeXmacs macros

\begin{document}

\noindent The 2nd MCI group Project client meeting will be held online\.{}(MS Team) on 07/03/2022 at 12:00PM

\

\title{Agenda}
\author{}
\date{}
\pagestyle{empty}
% Add text before \maketitle, make \newpage a "no-op"
{\let\newpage\relax\maketitle}

\noindent\tmtextbf{Chair:} \ Zhibin Liao

\noindent\tmtextbf{Members:} Andrew Butenko, Yu Zhang, Changyu Kang

\

\section{Apologies}

None.

\section{Presentation}

Discuss summary provided by client.

\subsection{Functional requirements and Presentations in Last Meeting}

Discussion on team availability, and first milestone. Introducing yourself,
sharing thoughts and ideas. Organizing regular stand-ups with the following structure:
\begin{itemizedot}
  \item What has been Done?
  
  \item What is in Progress?
  
  \item What still must be Done?
  
  \item Any Blockages/Expectations, etc.
\end{itemizedot}

\subsection{Problems and solutions}

Focus on SRS spec building. Client demonstration of existing solution
environment.

\section{Requirements Elicitation}

\tmtextbf{Project Process:}
\begin{itemizedot}
  \item Software Requirements Specification (SRS): user/system,
  functional/non-functional.
  
  \item Business plan: pitch presentation, business case, group activities.
  
  \item Software Project Management Plan (SPMP): scope, agenda and minutes,
  timesheets, coding
  
  \item Software Testing plan, quality assurance
\end{itemizedot}
\tmtextbf{Work tracking and communication:}
\begin{itemizedot}
  \item Project management model:
  \href{https://docs.microsoft.com/en-us/azure/devops/boards/best-practices-agile-project-management?view=azure-devops&tabs=agile-process}{Lightweight Agile or Basic}
  
  \item Meetings (MS Teams/live) with continuous feedback
  
  \item Project DevOps site with synchronized GitHub repository
  \href{https://dev.azure.com/a1712462/Containerization of ML models/_workitems/recentlyupdated/}{Boards}
  
  \item Delivery plans and milestones
  
  \item Risk assessment, options, and negotiations
\end{itemizedot}
\tmtextbf{Architectural Design:}
\begin{itemizedot}
  \item Model life cycle management
  
  \item Architecture and design patterns
  
  \item Interfaces: SOA, serverless, REST/GraphQL, file
  
  \item Resources: computation, storage, database
  
  \item UI/UX/API
  
  \item Pipelines: Docker, unit tests, CI/CD
  
  \item Environments
\end{itemizedot}

\section{Other Issues}

Questions for the next milestone. Client (Zhibin Liao) communication has being
established. This will be done in week 3.

\vspace{3em}

\noindent\tmtextbf{Note:} Next meeting will be held on 18/03/2022 at 11:30AM

\end{document}
